Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
fixed

plot_path <- here::here("other", "plots", "election_map.png")

@@

election_results %>%
  kable("html", caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold

>>>>

plot_path <- here::here("other", "plots", "election_map.pdf")

@@

election_results %>%
  kable(caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold
